\Title

### 2019-10-04 manuscript/manuscript.tex
Format manuscript without GJI style for archival

\documentclass[extra,mreferee]{gji}
%\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}
% To make two column figures appear in the correct order
\usepackage{fixltx2e}
% To make annotations on the sides
\usepackage{todonotes}

% Document metadata
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Title}{
    Fast non-linear gravity inversion in spherical coordinates
    with application to the South American Moho
}
\newcommand{\Keywords}{
    Inverse theory;
    Gravity anomalies and Earth structure;
    Satellite gravity;
    South America;
}
\title[]{\Title}
\author[]{
    Leonardo Uieda$^{1,2}$,
    Valéria C. F. Barbosa$^{2}$
    \\
    $^1$Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.
    e-mail: leouieda@gmail.com
    \\
    $^2$Observatório Nacional, Rio de Janeiro, Brazil.
}
% Metadata for the generated PDF
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{
    pdftitle={\Title},
    pdfauthor={Leonardo Uieda (leouieda@gmail.com)},
    pdfsubject={},
    pdfkeywords={\Keywords},
    pdfcreator={pdfTeX},
    allcolors=black,
}

@@

\label{firstpage}
\maketitle

@@

\noindent\textbf{Key words:} \Keywords

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/problem-concept}
    \caption{
        Sketch of the stages in gravity data correction and
        the discretization of the anomalous Moho relief using tesseroids.
        (a) The Earth and the measured gravity at point P ($g(P)$).
        (b) The Normal Earth and the calculated normal gravity at point P
        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
        (c) The gravity disturbance ($\delta(P)$) and the corresponding density
        anomalies after removal of the normal gravity: topography, oceans,
        crustal and mantle heterogeneities, and the anomalous Moho.
        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
        correction and the remaining density anomalies.
        (e) All density anomalies save the anomalous Moho are assumed to have
        been removed before inversion.
        (f) The discretization of the anomalous Moho in tesseroids. Grey
        tesseroids will have a negative density contrast while red tesseroids
        will have a positive one.
    }
    \label{fig:anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/cv-grid-separation}
    \caption{Sketch of a data grid separated into
        the training (open circles)
        and testing (black dots) data sets.
        The training data set is still displayed on a regular grid
        but with twice the grid spacing
        of the original data grid.}
    \label{fig:grid_separation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/synthetic-simple-data}
    \caption{
        A simple Moho model made of tesseroids for synthetic data application.
        (a) The Moho depth of the model in kilometers.
        The model transitions from a deep Moho in the right to a shallow Moho in
        left, simulating the transition between a continental and an oceanic
        Moho.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model
        shown in (a).
    }
    \label{fig:simple-data}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/south-america-cv}
    \caption{
        Cross-validation results for the South American Moho inversion.
        (a) Cross-validation to determine the regularization parameter $\mu$
        (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}),
        shown as a red triangle,
        corresponds to $\mu = 10^{-10}$.
        (b) Validation to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colors represent the Mean Square Error (Eq.~\ref{eq:msehyper}).
        The minimum (red triangle) is found at $z_{ref} = 35\ km$
        and $\Delta\rho = 400\ kg/m^3$.
    }
    \label{fig:sam-cv}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-moho}
    \caption{
        The estimated Moho depth of South America.
        Dotted lines represent the boundaries between major geologic provinces
        \citep[after][]{assumpcao2013a, goutorbe2015};
        AD: Andean Province,
        AFB: Andean foreland basins,
        AM: Amazonas Basin,
        BR: Brazilian Shield,
        BO: Borborema province,
        CH: Chaco Basin,
        GB: Guyana Basin,
        GU: Guyana Shield,
        PB: Parnaíba Basin,
        PC: Parecis Basin,
        PR: Paraná Basin,
        PT: Patagonia province,
        SF: São Francisco Craton,
        SM: Solimões Basin.
        Solid orange lines mark the limits of the main lithospheric plates
        \citep{bird2003};
        AF: Africa Plate,
        AN: Antarctica Plate,
        CA: Caribbean Plate,
        CO: Cocos Plate,
        SA: South America Plate,
        SC: Scotia Plate,
        NZ: Nazca Plate.
        The solid light grey line is the 35 km Moho depth contour.
    }
    \label{fig:sam-moho}
\end{figure*}

>>>>

\documentclass[twocolumn]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left=0.7in,right=0.7in,top=1.3in,bottom=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

% Document metadata
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Title}{
    Fast non-linear gravity inversion in spherical coordinates
    with application to the South American Moho
}
\newcommand{\Keywords}{
    Inverse theory;
    Gravity anomalies and Earth structure;
    Satellite gravity;
    South America;
}
\newcommand{\Author}{Uieda, L. and Barbosa, V.C.F.}
\newcommand{\AuthorAffil}{
    {\large
        Leonardo Uieda$^{1,2,*}$
        and
        Val\'eria C. F. Barbosa$^{2}$
    }
    \\[0.4cm]
    {\small $^1$ Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.}
    \\
    {\small $^2$ Observat\'orio Nacional, Rio de Janeiro, Brazil.}
    \\
    {\small $^*$ e-mail: leouieda@gmail.com}
}
\newcommand{\Journal}{Geophysical Journal International}
\newcommand{\Year}{2017}
\newcommand{\DOI}{10.1093/gji/ggw390}
\newcommand{\DOILink}{\href{https://doi.org/\DOI}{doi.org/\DOI}}

\setlength{\columnsep}{2\columnsep}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
    pdfkeywords={\Keywords},
}
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{}, \Year{}, doi:\DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

@@

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2016 October 13. Received in original form 2016 March 24.
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article
    published in \textit{\Journal} following peer review.
    The version of record
    ``\textit{\Author{} (\Year{}). \Title{}. \Journal{}. doi:\DOI{}}''
    is available online at: \DOILink{}.
}

\maketitle

@@

\vspace{0.4cm}
\noindent\textbf{Key words:} \Keywords

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/problem-concept}
    \caption{
        Sketch of the stages in gravity data correction and
        the discretization of the anomalous Moho relief using tesseroids.
        (a) The Earth and the measured gravity at point P ($g(P)$).
        (b) The Normal Earth and the calculated normal gravity at point P
        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
        (c) The gravity disturbance ($\delta(P)$) and the corresponding density
        anomalies after removal of the normal gravity: topography, oceans,
        crustal and mantle heterogeneities, and the anomalous Moho.
        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
        correction and the remaining density anomalies.
        (e) All density anomalies save the anomalous Moho are assumed to have
        been removed before inversion.
        (f) The discretization of the anomalous Moho in tesseroids. Grey
        tesseroids will have a negative density contrast while red tesseroids
        will have a positive one.
    }
    \label{fig:anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/cv-grid-separation}
    \caption{Sketch of a data grid separated into
        the training (open circles)
        and testing (black dots) data sets.
        The training data set is still displayed on a regular grid
        but with twice the grid spacing
        of the original data grid.}
    \label{fig:grid_separation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/synthetic-simple-data}
    \caption{
        A simple Moho model made of tesseroids for synthetic data application.
        (a) The Moho depth of the model in kilometers.
        The model transitions from a deep Moho in the right to a shallow Moho in
        left, simulating the transition between a continental and an oceanic
        Moho.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model
        shown in (a).
    }
    \label{fig:simple-data}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/south-america-cv}
    \caption{
        Cross-validation results for the South American Moho inversion.
        (a) Cross-validation to determine the regularization parameter $\mu$
        (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}),
        shown as a red triangle,
        corresponds to $\mu = 10^{-10}$.
        (b) Validation to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colors represent the Mean Square Error (Eq.~\ref{eq:msehyper}).
        The minimum (red triangle) is found at $z_{ref} = 35\ km$
        and $\Delta\rho = 400\ kg/m^3$.
    }
    \label{fig:sam-cv}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{figures/south-america-moho}
    \caption{
        The estimated Moho depth of South America.
        Dotted lines represent the boundaries between major geologic provinces
        \citep[after][]{assumpcao2013a, goutorbe2015};
        AD: Andean Province,
        AFB: Andean foreland basins,
        AM: Amazonas Basin,
        BR: Brazilian Shield,
        BO: Borborema province,
        CH: Chaco Basin,
        GB: Guyana Basin,
        GU: Guyana Shield,
        PB: Parnaíba Basin,
        PC: Parecis Basin,
        PR: Paraná Basin,
        PT: Patagonia province,
        SF: São Francisco Craton,
        SM: Solimões Basin.
        Solid orange lines mark the limits of the main lithospheric plates
        \citep{bird2003};
        AF: Africa Plate,
        AN: Antarctica Plate,
        CA: Caribbean Plate,
        CO: Cocos Plate,
        SA: South America Plate,
        SC: Scotia Plate,
        NZ: Nazca Plate.
        The solid light grey line is the 35 km Moho depth contour.
    }
    \label{fig:sam-moho}
\end{figure*}
